The College Application Problem

### 2022-06-10 slides_25min/slides.tex
25min script, typos

\definecolor{teal}{HTML}{008080}
\definecolor{olivedrab}{HTML}{6b8e23}
\definecolor{crimson}{HTML}{b22222}
\definecolor{palettetertiary}{HTML}{4169E1}
\definecolor{beige}{HTML}{f5fffa}
\definecolor{azure}{HTML}{F5F5F5}
\definecolor{rebeccapurple}{HTML}{663399}

@@

A branch-and-bound algorithm may be necessary to handle more advanced constraint structures.
\else
이 기반으로 만든 간단한 알고리즘은 작은 ($m \leq 35$) 인스턴스에 괜찮지만 분지 마디를 선택하는 휴리스틱으로 \textbf{개선할 여지가} 보인다.

@@

>>>>

\definecolor{teal}{HTML}{008080}
\definecolor{olivedrab}{HTML}{6b8e23}
\definecolor{crimson}{HTML}{b22222}
\definecolor{palettetertiary}{HTML}{4169E1}
\definecolor{beige}{HTML}{f5fffa}
\definecolor{azure}{HTML}{F5F5F5}
\definecolor{rebeccapurple}{HTML}{663399}
\definecolor{lightslategray}{HTML}{778899}

@@

% Clone of slide above but with BnB grayed out
\ifen {
\begin{frame}{Algorithms for Ellis's problem}

The general problem is \textbf{NP-complete} (reduction from knapsack). We offer four algorithms:
\begin{itemize}
\item \textcolor{lightslategray}{A linear relaxation and \textbf{branch-and-bound scheme} allow us to interface with existing INLP solvers. \hfill{\footnotesize (see appendix)}}

4개의 알고리즘 제시:
\begin{itemize}
\item \textcolor{lightslategray}{선형 완화 문제와 해당 \textbf{분지한계} (branch-and-bound) 해법. 일반적인 INLP 문제에 대해 자주 쓰이는 방법이다. \hfill{\footnotesize (부록)}}

@@

A branch-and-bound algorithm may be necessary to handle more advanced constraint structures.
\else
이 기반으로 만든 간단한 알고리즘은 작은 ($m \leq 35$) 인스턴스에 대해 괜찮지만 분지 마디를 선택하는 휴리스틱으로 \textbf{개선할 여지가} 보인다.
